On The Impact of Atoms of Confusion in JavaScript Code

### 2021-01-25 2_Background.tex
sincronizando o github

The concept of program comprehension is central to software maintenance and feature development \cite{DBLP:conf/iwpc/TilleySP96}. Regardless of whether they are performing maintenance on legacy software or adding new features, programmers have to understand what the source code does before making any improvements. A natural consequence of this is that a programmer must also have in mind that other programmers (or their future selves) are going to have to spend time trying to understand the code being currently developed before doing any work themselves.

@@

Santos and Gerosa~\cite{Santos:2018:ICP} analyze the impact of eleven coding practices on program readability. Some of them, such as avoiding more than three levels of code
block nesting, are atom candidates. This work evaluates the coding practices solely based on personal opinions of the study subjects. Furthermore, it focuses on the Java language. Finally, most of the practices are more related to code formatting than language constructs or idioms.

>>>>

The concept of program comprehension is central to software maintenance and feature development \cite{DBLP:conf/iwpc/TilleySP96}. Regardless of whether they are performing maintenance on legacy software or adding new features, programmers have to understand what the source code does before making any improvements. A natural consequence of this is that a programmer must also have in mind that other programmers (or their future selves) 
%are going to have to
will
spend time trying to understand the code being currently developed before doing any work themselves.

@@

Santos and Gerosa~\cite{Santos:2018:ICP} analyze the impact of eleven coding practices on program readability. Some of them, such as avoiding more than three levels of code
block nesting, are atom candidates. 
% Diego: Troquei "this work" para "their work". Removi o "more" de "are more related"
Their work evaluates the coding practices solely based on personal opinions of the study subjects. Furthermore, it focuses on the Java language. Finally, most of the practices are related to code formatting than language constructs or idioms.

### 2021-01-25 3_Method.tex
sincronizando o github

In the firt study we explore the impact of atoms of confusion on
understanding JavaScript code, by answering two questions: (a) \emph{Do code snippets that contain atoms of confusion produce a higher misunderstanding rate when programmers try to predict their outcome?} and (b) \emph{Do code snippets with atoms of confusion require programmers to take longer to predict their output?}
Since JavaScript and C have some constructs in common (Section~\ref{sec:aoc}), we first selected a set of atoms of confusion for the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} whose idioms also exist in JavaScript programs. Appendix~\ref{sec:appendix-atoms} summarizes all atoms we consider in our research.

>>>>

In the first study we explore the impact of atoms of confusion on
understanding JavaScript code, by answering two questions: (a) \emph{Do code snippets that contain atoms of confusion produce a higher misunderstanding rate when programmers try to predict their outcome?} and (b) \emph{Do code snippets with atoms of confusion require programmers to take longer to predict their output?}
Since JavaScript and C have some constructs in common (Section~\ref{sec:aoc}), we first selected a set of atoms of confusion for the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} whose idioms also exist in JavaScript programs. Appendix~\ref{sec:appendix-atoms} summarizes all atoms we consider in our research.
